Digital Analysis of Paintings

### 2014-05-07 paper.tex
Add paper 15.

>>>>

To merge the segmented regions a region merging criterion $\epsilon$ is
calculated. $\epsilon$ is then used to merge adjacent regions from highest to
lowest. $\epsilon$ is calculated in terms of the differences in colour
distribution between the regions and the similarity to the catalogue of
brushstrokes.

Once this process is complete, the strokes can then be refined and vectorised
for the animation process.

This paper also considers the separation of overlapping strokes to be able to
animate them naturally, but this could potentially be used for further
analysis. The overlapping regions can be identified in the segmentation process
then have an iterative algorithm which separates the colours of the overlapping
region. Because the colouring of an overlapping region can be the mixture of
more than a single colour, a mixture model is used to model the overlapping
strokes.

Combining this with the library of known strokes can be used to get a good
estimate of the separate strokes.

This paper presents some really interesting research into the decomposition of
paintings using brushstroke extraction; but is very specific to Chinese
paintings. An example failure run on a painting by Georges Seurat shows the
overfitting which this method falls prey to.

The reliance of a catalogue of brushstrokes seems to do more harm than good in
some circumstances, the authors do note that the catalogue is by no means
exhaustive. This is what seems to lead to the over segmentation. Perhaps
learning the strokes from existing work as discussed in \cite{van2010texton}
could provide more generalised results.

Unlike \cite{jia12rhythmic}, the extracted strokes are not evaluated against a
ground truth. Even so, the visualisation of the segmented brush strokes seems
reasonable and to be able to complete the animation steps there must be some
validity to the extraction process.

The development of a technique to discriminate two overlapping strokes shows
some potential, although there is no real verification of the method to do
some. It should also be noted that the paper only considers two overlapping
strokes as more would become too computationally complex to complete in a
reasonable time.
